---
title: "Alternative Ability Text Analysis Project"
author: "Danielle Strauss"
date: "August 22, 2018"
output: html_document
---
Loading Packages
```{r}
library(quanteda)
library(readr)
library(tidytext)
library(tidyverse)
library(dplyr)
library(purrr)
library(tm)
library(psych)
```

Set working directory
```{r cars}
setwd("C:/Users/dstrauss/Documents/MentalHealthTextAnalysis")
getwd()

```

Retrieve all files in working directory ending with ".txt"
```{r}
setinterviews <- list.files(pattern = ".txt")
```

Create a list with all the interview files
```{r}
interviews <- map_df(list.files("", full.names = TRUE), 
                     read_tsv, col_names = FALSE)
```

Steps to get interview text associated with specific interview
```{r}
my.import <- function(data) {
  my.df <- read_tsv(data, col_names = FALSE)
  names(my.df) <- "Report" 
  my.df$Name <- as.factor(data)
  return(my.df)
}

interviews <- lapply(setinterviews, my.import)

interviews <- do.call("rbind", interviews)
```

Clean interview data set without NAs
```{r}
clean_interview <- interviews %>% 
  filter(!is.na(Report))

#Tidy Interviews
tidy_interviews <- clean_interview %>% 
  unnest_tokens(word, Report, token = "words")
```

Read in Excel files
```{r}
#DevDisWordKey <- read_csv("filename.csv", col_names = TRUE)
#MHWordKey <- read_csv("filename.csv", col_names = TRUE)

```

Search for one word using Mental Health and Developmental Disability Word Keys
```{r}
one_dev <- tidy_interviews %>% 
  count(Name, word) %>%
  inner_join(DevDisWordKey)

one_mh <- tidy_interviews %>%
  count(Name, word) %>%
  inner_join(MHWordKey)
```

Create a binary for developmental disability words
```{r}
one_dev$autism <- 1
one_dev$autism <- if_else(one_dev$word == "autism", 1, 0)
one_dev$adhd <- 1
one_dev$adhd <- if_else(one_dev$word == "adhd", 1, 0)
one_dev$add <- 1
one_dev$add <- if_else(one_dev$word == "add", 1, 0)
one_dev$aspergers <- 1
one_dev$aspergers <- if_else(one_dev$word == "aspergers", 1, 0)
one_dev$iep <- 1
one_dev$iep <- if_else(one_dev$word == "iep", 1, 0)
```

Add mental health key Words to one_dev data frame
```{r}
one_dev$anxiety <- 0
one_dev$depression <- 0
one_dev$bipolar <- 0
one_dev$anorexia <- 0
one_dev$bulimia <- 0
one_dev$ocd <- 0
one_dev$schizophrenia <- 0
one_dev$ptsd <- 0
one_dev$trauma <- 0
one_dev$therapist <- 0
one_dev$therapy <- 0
one_dev$neglect <- 0
one_dev$abuse <- 0
one_dev$bullying <- 0
one_dev$psychiatrist <- 0
one_dev$counselor <- 0
```

Creating a binary for mental health words
```{r}
one_mh$anxiety <- 1
one_mh$anxiety <- if_else(one_mh$word == "anxiety", 1, 0)
one_mh$depression <- 1
one_mh$depression <- if_else(one_mh$word == "depression", 1, 0)
one_mh$bipolar <- 1
one_mh$bipolar <- if_else(one_mh$word == "bipolar", 1, 0)
one_mh$anorexia <- 1
one_mh$anorexia <- if_else(one_mh$word == "anorexia", 1, 0)
one_mh$bulimia <- 1
one_mh$bulimia <- if_else(one_mh$word == "bulimia", 1, 0)
one_mh$ocd <- 1
one_mh$ocd <- if_else(one_mh$word == "ocd", 1, 0)
one_mh$schizophrenia <- 1
one_mh$schizophrenia <- if_else(one_mh$word == "schizophrenia", 1, 0)
one_mh$ptsd <- 1
one_mh$ptsd <- if_else(one_mh$word == "ptsd", 1, 0)
one_mh$trauma <- 1
one_mh$trauma <- if_else(one_mh$word == "trauma", 1, 0)
one_mh$therapist <- 1
one_mh$therapist <- if_else(one_mh$word == "therapist", 1, 0)
one_mh$therapy <- 1
one_mh$therapy <- if_else(one_mh$word == "therapy", 1, 0)
one_mh$neglect <- 1
one_mh$neglect <- if_else(one_mh$word == "neglect", 1, 0)
one_mh$abuse <- 1
one_mh$abuse <- if_else(one_mh$word == "abuse", 1, 0)
one_mh$bullying <- 1
one_mh$bullying <- if_else(one_mh$word == "bullying", 1, 0)
one_mh$psychiatrist <- 1
one_mh$psychiatrist <- if_else(one_mh$word == "psychiatrist", 1, 0)
one_mh$counselor <- 1
one_mh$counselor <- if_else(one_mh$word == "counselor", 1, 0)
```

Add developmental disability words to one_mh
```{r}
one_mh$autism <- 0
one_mh$adhd <- 0
one_mh$add <- 0
one_mh$aspergers <- 0
one_mh$iep <- 0
```

Merge one_mh and one_dev
```{r}
one_word <- rbind(one_dev, one_mh)

sparse_words <- one_word %>% 
  cast_sparse(Name, word, n)
```

Exact names are combined into a data frame
```{r}
x <- as.data.frame(as.matrix(sparse_words))
summary(x)
```

Sum all rows
```{r}
x$sum <- rowSums(x) 
```

Calculate number of Alternative Abilities
```{r}
x$AltAb <- x$sum > 8

sum(x$AltAb)
```
