---
title: "Markdown of Practice Interviews"
author: "Danielle Strauss"
date: "July 18, 2018"
output: html_document
---

```{Loading Packages}
library(quanteda)
library(readr)
library(tidytext)
library(tidyverse)
library(dplyr)
library(purrr)
library(tm)
```

Mental Health Files are in the Data from R One Drive File

```{Set working directory}
setwd("C:/Users/dstrauss/Documents/MentalHealthTextAnalysis")
setinterviews <- list.files(pattern = ".txt")
```



```{Create List with all the Files}
interviews <- map_df(list.files("C:\\Users\\dstrauss\\Documents\\MentalHealthTextAnalysis", full.names = TRUE), 
                     read_tsv, col_names = FALSE)
```

#Steps to get interview text associated with specific interview
```my.import <- function(data) {
  my.df <- read_tsv(data, col_names = FALSE)
  names(my.df) <- "Report" 
  my.df$Name <- as.factor(data)
  return(my.df)
}
interviews <- lapply(setinterviews, my.import)
interviews <- do.call("rbind", interviews)
```

#Clean Interview data set that does not include NAs
```clean_interview <- interviews %>% filter(!is.na(Report))
```

```{r Tidying Interviews for one word and two word tokens}
tidy_interviews <- interviews %>% unnest_tokens(word, Report, token = "words")
tidy_interviews_ngram <- clean_interview %>% 
  unnest_tokens(bigram, Report, token = "ngrams", n = 2)
```
#Tidy Interviews
```
tidy_interviews <- clean_interview %>% unnest_tokens(word, Report, token = "words")
tidy_interviews_ngram <- clean_interview %>% 
  unnest_tokens(bigram, Report, token = "ngrams", n = 2)
```

#Read in Excel Files (in Data from R File)
```{r Bigram search for dev disabilities and mental health}
DevDisWordKey <- read_csv("DevelopmentalDisabilityWordKey.csv", col_names = TRUE)
MHWordKey <- read_csv("MentalHealthWords.csv", col_names = TRUE)

```
#Searching for one word using Mental Health and Developmental Disability Word Keys
```
one_dev <- tidy_interviews %>% 
  count(Name, word) %>%
  inner_join(DevDisWordKey)
one_mh <- tidy_interviews %>%
  count(Name, word) %>%
  inner_join(MHWordKey)
```
#Searching for Multiple Words using Mental Health and Developmental Disability Word Keys
```
bigrams.separated.before <- tidy_interviews_ngram %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bi_dev <- bigrams.separated.before %>%
  filter((word1 %in% c("developmental", "autism", "behavioral", "applied", "behavior", "intellectual", "occupational", "speech")), word2 %in% c("disability", "spectrum", "disorder", "behavior", "interventionist", "intervention", "delay", "therapist", "therapy"))

bi_mh <- bigrams.separated.before %>%
  filter((word1 %in% c("emotional", "behavioral", "sexual", "domestic", "bipolar", "eating", "mental", "panic", "anxiety")), word2 %in% c("difficulties", "abuse", "violence", "disorder", "health", "illness", "attack"))
```
